CIVILITY: Cloud based Interactive Visualization of Tractography Brain Connectome

### 2016-07-12 doc/spiePaper/article.tex
DOC : update spie paper

- CIVILITY-tractography ; analysis pipeline. The analysis of the brain connectome is computed with a probabilistic tractography method (FSL tools : bedpostx and probtrackx2) using surfaces as seeds. Seeds surfaces are created with the ExtractLabelSurfaces\footnote{https://github.com/NIRALUser/ExtractLabelSurfaces}.

>>>>

- CIVILITY-tractography ; analysis pipeline. The analysis of the brain connectome is computed using a probabilistic tractography method (FSL tools : bedpostx and probtrackx2) using surfaces as seeds. Seeds surfaces are created with the ExtractLabelSurfaces\footnote{https://github.com/NIRALUser/ExtractLabelSurfaces}.
